Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.4.0, major revision.

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show its outperforming to Wide-ResNet
which inspired from unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in 1960s, and had its implementation in 1980s,
and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
Wide-ResNet~\cite{zagoruyko2016wide}, ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2019pre, cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2018bert} and RoBERTa~\cite{liu2019roberta} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.

@@

\par Given an unlabeled dataset $\Bbb X$, the BERT objective samples a sub-sequence $\Bbb S \in \{C\}$,
$C$ represents all possible tokens, and such that for each index $i \in \Bbb S$,
there is independent probability $15\%$ of appearing in $\Bbb S$,
name the token $M$ as the BERT mask.
Train the language model by minimizing the BERT objective of the "masked" elements $x_M$
conditioned on the "unmasked" ones $x_{\left[1,n\right]\backslash M}$.
\[
  \lambda = \mathop{\Bbb E}\limits_{x\sim\Bbb X} \mathop{\Bbb E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
\]

@@

I design a simple classification models without too many layers, as Figure-1 shows.
And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:
\begin{itemize}
\item {\bf Input layer}
\item {\bf Concat layer}
\item {\bf Trim layer}
\item {\bf Encoder layer}
\item {\bf Embedding layer}
\item {\bf Feature Extraction layer}
\item {\bf Output layer}
\end{itemize}

\par The CIFAR-10 dataset contains 60000 colour images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other meta-data if provided, as a sequence of ASCII character.
In the Concat layer, the pixel-channel value and meta data are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel vules and meta values, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of BERT language model, sequence larger than $512$ need to be trimmed before sending to BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contrains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer is used.
In the Output layer, the classification label of the image is feed in the model.

@@

As Cui \etal~\cite{cui2019pre} reported that the training of RBT3 language model was based on Devlin \etal's
Chinese BERT-base language model and the training of RBTL3 and RoBERTa-large language model used randomized initialization.
Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
The dropout rate is $0.05$.

@@

>>>>

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show its outperforming to Wide-ResNet
which inspired from unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in 1960s, and had its implementation in 1980s,
and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
Wide-ResNet~\cite{zagoruyko2016wide}, ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2019pre, cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2018bert} and RoBERTa~\cite{liu2019roberta} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.
  He and Peng~\cite{he2017fine} combined vision stream and language stream as two parallel channels for extracting multi-source information in the imaege classification,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.

@@

\par Given an unlabeled dataset $\Bbb X$, the BERT objective samples a sub-sequence $\Bbb S \in \{C\}$,
$C$ represents all possible tokens, and such that for each index $i \in \Bbb S$,
there is independent probability $15\%$ of appearing in $\Bbb S$,
name the token $M$ as the BERT mask.
Train the language model by minimizing the BERT objective of the "masked" elements $x_M$
conditioned on the "unmasked" ones $x_{\left[1,n\right]\backslash M}$.

\begin{equation}
  \lambda = \mathop{\Bbb E}\limits_{x\sim\Bbb X} \mathop{\Bbb E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
\end{equation}

@@

I design a simple classification models without too many layers, as Figure-1 shows.
And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:

\begin{itemize}
\item {\bf Input layer}
\item {\bf Concat layer}
\item {\bf Trim layer}
\item {\bf Encoder layer}
\item {\bf Embedding layer}
\item {\bf Feature Extraction layer}
\item {\bf Output layer}
\end{itemize}

\par The CIFAR-10 dataset contains 60000 colour images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other meta-data if provided, as a sequence of ASCII character.
In the Concat layer, the pixel-channel value and meta data are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel vules and meta values, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of BERT language model, sequence larger than $512$ need to be trimmed before sending to BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contrains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation-2, is used.
In the Output layer, the classification label of the image is feed in the model.

\begin{equation}
  \sigma(\textbf{z})_j = {e^{\textbf{z}_j} \over {\sum_{k=1}^{\textit{K}} e^{\textbf{z}_k}}}, j=1,\cdots,\textit{K}.
\end{equation}
%-------------------------------------------------------------------------

@@

As Cui \etal~\cite{cui2019pre} reported that the training of RBT3 language model was based on Devlin \etal's
Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
The dropout rate is $0.05$.

@@

\par The experiment was performed on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of high speed of memory each,
which can provide 420 tera-flops of computation capability.
